\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-04 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

The referee writes: \textit{A more natural approach is what the authors, at some point, refer to as the Hummel's Methodology. That is, one can alternatively estimate the share of the additive component as:}
$$\frac{t_{ik}}{ (\tau_{ik}-1)\tilde{p}_{ik} + t_{ik}} = \beta_{ik}$$

\textit{where $\beta_{ik}$ is the elasticity of transport costs w.r.t. unit price. Given the authors' objective and the data they are using, $\beta$ can be separately estimated for each industry-country pair using the following regression:}

\begin{equation}
\ln f_{ikd} = \beta_{is(k)}\ln \tilde{p}_{ikd} + \text{Controls}_{ikd} +\epsilon_{ikd} \label{eq:estimation_ref1}
\end{equation}

\textit{where $d$ denotes the US district of entry and $k$ denotes an HS10 product} ($f_{ikd}$ being the transport costs). \textit{The
identification of $\beta_{ik}$, in this case, would rely on the across HS10 product and
district-of-entry variation in $f_{ik}$ and $p_{ik}$. Estimating the above equation would
obviously require that the authors do not aggregate up the raw Census data
across all districts and all 10-digit products pertaining to the same 5-digit category. [...] The first advantage of this so-called Hummel's approach is that the above regression can be estimated separately for various country-industry pairs, without imposing Assumptions (a) and (b) outlined above.}

@@

\paragraph{Estimating the share of additive costs: Highlighting some requirements} Our estimated equation relies on non-linear estimation methods, such as Non-Linear Least Squares. However, even with another formulation, such as the one suggested by the referee in Equation (\ref{eq:estimation_ref1}), we would still be constrained to resort to non-linear estimators. This is due to the necessity of imposing an \textit{ex-ante} restriction on parameters, i.e. $\tau \geq 1$ and $t \geq 0$, or $0 \leq  \beta \leq 1$. Should we relax these restrictions, standard linear, least squares estimates often deliver negative, meaningless estimates. In this respect, implementing the referee's method (see below) does not suppress the requirement of resorting on non-linear estimates (and the computational, time-consuming burden it induces). Imposing this parameters constraint was not made clear enough in the initial version, and we did our best to make this very important justification clearer in the revised version, as it is now exposed in footnote \textbf{12 page 8}. \textbf{LP: A Ai enleve le copie-colle de la footnote dans la lettre; il suffit de dire que c'est dans la version revisee, non?}\smallskip

\paragraph{Exploring Referee's alternative functional form \label{subsec:functional_form}}

The estimation strategy suggested by the referee starts from Equation (\ref{eq:Hummels}) linking transport costs and unit prices as assumed in Hummels (2007), yielding Equation (\ref{eq:estimation_ref1}) as estimation equation. By year and transport mode, this implies running the estimation for each country of origin $i$ and each sector $s(k)$ = 3 digit sector, exploiting the variability between sub-sectors at the 10-digit level ($k$) and between ports of entry in the US ($d$). As previously noticed, running this estimation limits the time coverage as information is available at the HS-10 only since 2001. We have thus run referee's method over the years 2005-2013, at the $s=3, k=10$ sectoral/product levels, and reported the results in the Online Appendix.

Notice that we are aware of the referee's suggestion to run his/her estimation strategy considering sectoral aggregation at the 5-digit level (with $k=10$). We yet keep considering sectors at the 3-digit aggregation level, in view of being able to compare the pros and cons of the referee's method versus ours, including those years for which the finest disaggregation level is $k=5$ (i.e., the original Hummel's dataset over 1974-1988, as the US Bureau of census import database starts in 1989 --yet being effectively available since 2001 only because of the Covid situation.)

### 2021-10-04 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
Premier jet comparaison estimation beta_baseline
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
Pour tableaux de comparaison
beta et wgt/qy/baseline

Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
changement réponse et annexe online

In line with Table \ref{tab:robustness_separability}, the results shown in Figure \ref{fig:robustesse_non_separe} confirm that the separability assumption (retained in our baseline estimation) tends to overestimate the value of the additive cost component (and underestimate the value of the ad-valorem cost).
However, they also show that the difference is quantitatively small in most cases. Further, and most importantly, whatever the transport mode and for both types of transport costs, the trend patterns of international transport costs, whether estimated under the separability assumption or not, are very similar. Along with the quality-of-fit diagnosis, this confirms the robustness of our estimation results to this assumption.

\paragraph{Distribution of the $\beta$} As final check, we also investigate whether the varying pattern over time/country of origin/product pointed out in Section \ref{sec:results_decomposition} is also robust to the separability assumption. With this aim, we report in Figure \ref{fig:histogram_beta_robustness}
the histogram of the distribution of the elasticity of transport costs to the export price ($\beta_{ikt}$, for air transport (top panel) and for maritime transport (bottom panel) under the baseline specification (Panels (A), (c))) and the non-separability scenario (Panels (B), (c)).

@@

For both transport modes the distribution of $\beta_{ikt}$ over the triplet (year, country of origin, product) appears smoothly distributed over the interval $[0,1]$, whatever the assumption regarding the specification of fixed effects.
Relaxing the assumption that fixed effects are separable between the two country and product dimensions does not alter qualitatively our conclusion, that the elasticity of transport costs to the export price (or the share of additive costs in total transport costs), is strongly varying over time, countries of origin and products.
\footnote{As a consequence, this also provides an indirect robustness check to the results regarding the trend decomposition provided in Section \ref{sec:results_trends}, which establish that the decline of ``pure'' transport costs is a main reason for the decrease of overall transport costs observed over time.}

>>>>

In line with Table 2 of the paper, the results shown in Figure \ref{fig:robustesse_non_separe} confirm that the separability assumption (retained in our baseline estimation) tends to overestimate the value of the additive cost component (and underestimate the value of the ad-valorem cost).
However, they also show that the difference is quantitatively small in most cases. Further, and most importantly, whatever the transport mode and for both types of transport costs, the trend patterns of international transport costs, whether estimated under the separability assumption or not, are very similar. Along with the quality-of-fit diagnosis, this confirms the robustness of our estimation results to this assumption.

\paragraph{Distribution of the $\beta$} As final check, we also investigate whether the varying pattern over time/country of origin/product is also robust to the separability assumption. With this aim, we report in Figure \ref{fig:histogram_beta_robustness}
the histogram of the distribution of the elasticity of transport costs to the export price ($\beta_{ikt}$, for air transport (top panel) and for maritime transport (bottom panel) under the baseline specification (Panels (A), (c))) and the non-separability scenario (Panels (B), (c)).

@@

For both transport modes the distribution of $\beta_{ikt}$ over the triplet (year, country of origin, product) appears smoothly distributed over the interval $[0,1]$, whatever the assumption regarding the specification of fixed effects.
Relaxing the assumption that fixed effects are separable between the two country and product dimensions does not alter qualitatively our conclusion, that the elasticity of transport costs to the export price (or the share of additive costs in total transport costs), is strongly varying over time, countries of origin and products.
\footnote{As a consequence, this also provides an indirect robustness check to the results regarding the trend decomposition provided in Section 4 of the paper, which establish that the decline of ``pure'' transport costs is a main reason for the decrease of overall transport costs observed over time.}

\subsubsection{Estimating $\widehat{\beta_{i,s}}$ directly}

In this section, we explore an alternative estimation method, which proceeds as follows. $\beta$ can be separately estimated for each industry $s$-origin country $i$ using the following regression:

\begin{equation}
\ln TC_{ikd} = \beta_{is}\ln \tilde{p}_{ikd} + \text{Controls}_{ikd} +\epsilon_{ikd} \label{eq:estimation_ref1}
\end{equation}

where $d$ denotes the US district of entry and $k$ denotes an HS-10 product, $TC_{ikd}$ being the transport costs. The
identification of $\beta_{is}$, in this case, would rely on exploiting the variability between sub-sectors at the 10-digit
level ($k$) and between ports of entry in the US ($d$).

One advantage of this approach is that the above regression can be estimated separately for various country-industry pairs on a linear basis, without having to resort on the separability assumption. This does not solve the issue yet, for two main reasons. First, we would still be constrained to resort to non-linear estimators. This is due to the necessity of imposing an \textit{ex-ante} restriction on parameters, i.e. imposing $0 \leq  \beta \leq 1$. Should we relax this restriction, standard linear, least squares estimates often deliver negative, meaningless estimates. In this respect, implementing this does not suppress the requirement of resorting on non-linear estimates (and the computational, time-consuming burden it induces).

Second,

\begin{table}[htbp]
	\caption{Comparison 2005-2013}
	\begin{center}		
		\input{Comp_baseline_referee1_reshaped.tex}
	\end{center}
	\label{tab_comp_referee1_baseline}%
\end{table}%

\subsubsection{Weights and quantities}

\begin{table}[htbp]
	\caption{Comparison 2005-2019}
	\begin{center}		
		\input{Comp_baseline_wgt_qy.tex}
	\end{center}
	\label{tab_comp_referee1_baseline}%
\end{table}%
